LSOA domestic Electricty and Gas maps

### 2021-08-10 LSOA domestic Elec and Gas.Rmd
Filling in the gaps for cities in more detail

##### Looking at cities in more detail        
```{r Southampton LSOA dom Elec}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(lsoa_merged_sf, LAD11NM == "Southampton")

# plotting the electricity consumption of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `Mean domestic electricity consumption \n(kWh per meter)`)) +
  scale_fill_continuous(name = "Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Southampton")
```
```{r Portsmouth LSOA dom Elec}
#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
mapData <- dplyr::filter(lsoa_merged_sf, LAD11NM == "Portsmouth")

# plotting the electricity consumption of Portsmouth in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `Mean domestic electricity consumption \n(kWh per meter)`)) +
  scale_fill_continuous(name = "Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Portsmouth")
```
```{r Winchester LSOA dom Elec}
#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
mapData <- dplyr::filter(lsoa_merged_sf, LAD11NM == "Winchester")

# plotting the electricity consumption of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `Mean domestic electricity consumption \n(kWh per meter)`)) +
  scale_fill_continuous(name = "Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Winchester")
```
####Difference between 2010 and 2019 dom elec

here here

#####Cities in more detail

here here here

@@

# plotting the gas consumption of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Winchester")
```
####Difference between 2010 and 2019 dom gas

here here here

#####Cities in more detail

here here here

>>>>

##### Looking at cities in more detail        
```{r Southampton LSOA dom Elec}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(lsoa_merged_sf, LAD11NM == "Southampton")
# plotting the electricity consumption of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `Mean domestic electricity consumption \n(kWh per meter)`)) +
  scale_fill_continuous(name = "Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Southampton")
```
```{r Portsmouth LSOA dom Elec}
#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
mapData <- dplyr::filter(lsoa_merged_sf, LAD11NM == "Portsmouth")
# plotting the electricity consumption of Portsmouth in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `Mean domestic electricity consumption \n(kWh per meter)`)) +
  scale_fill_continuous(name = "Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Portsmouth")
```
```{r Winchester LSOA dom Elec}
#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
mapData <- dplyr::filter(lsoa_merged_sf, LAD11NM == "Winchester")

# plotting the electricity consumption of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `Mean domestic electricity consumption \n(kWh per meter)`)) +
  scale_fill_continuous(name = "Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Winchester")
```
####Difference between 2010 and 2019 dom elec
```{r Creating the difference in LSOA mean dom elec consumption variable}
domelec_LSOA_2010<-readr::read_csv(paste0(dataFolder,"energy/electricity/LSOA Dom Elec csv/LSOA_ELEC_2010.csv"))
domelec_LSOA_2019<-readr::read_csv(paste0(dataFolder, "energy/electricity/LSOA Dom Elec csv/LSOA_ELEC_2019.csv"))
domelec_LSOA_2010$de2010<-domelec_LSOA_2010$'Mean domestic electricity consumption \n(kWh per meter).x'
domelec_LSOA_2019$de2019<-domelec_LSOA_2019$'Mean domestic electricity consumption \n(kWh per meter).y'
merged_de<-merge(domelec_LSOA_2010, domelec_LSOA_2019, by="Middle Layer Super Output Area (MSOA) Code", all=TRUE)
names(merged_de)
merged_de$de_diff<-as.numeric(merged_de$de2019)-as.numeric(merged_de$de2010)##BROKEN
summary(merged_de)
```

```{r Mapping the LSOA difference in mean dom elec consumption}
merged_de$LSOA11CD<-merged_de$"Middle Layer Super Output Area (MSOA) Code"
lsoa_de20102019<-merge(lsoa_sf_data, merged_de)
ggplot2::ggplot(lsoa_de20102019)+geom_sf(aes(fill="de_diff")+scale_fill_continuous(name="Change in Mean comsumpton (kWh per meter)"),low="green",high="red")+labs(caption="Solent(all LSOAs)")
##BROKEN
```

#####Cities in more detail
```{r Southampton LSOA difference in dom Elec}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(merged_de, LAD11NM == "Southampton")
# plotting the electricity consumption of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `de_diff`)) +
  scale_fill_continuous(name = "Change in Mean comsumpton (kWh per meter)", low = "green", high = "red") +
  labs(caption = "Southampton")
```
```{r Portsmouth LSOA difference in dom Elec}
#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
mapData <- dplyr::filter(merged_de, LAD11NM == "Portsmouth")
# plotting the electricity consumption of Portsmouth in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `de-diff`)) +
  scale_fill_continuous(name = "Change in Mean comsumpton (kWh per meter)", low = "green", high = "red") +
  labs(caption = "Portsmouth")
```
```{r Winchester LSOA difference in dom Elec}
#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
mapData <- dplyr::filter(merged_de, LAD11NM == "Winchester")
# plotting the electricity consumption of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `de_diff`)) +
  scale_fill_continuous(name = "Change in Mean comsumpton (kWh per meter)", low = "green", high = "red") +
  labs(caption = "Winchester")
```

@@

# plotting the gas consumption of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Winchester")
```
####Difference between 2010 and 2019 dom gas 
```{r Creating the dfference in LSOA dom gas consumption variable}
#Green indicates a decrease in gas consumption from 2010 to 2019
#Red indicates an increase in gas consumption from 2010 to 2019
dgas_LSOA_2010 <- readr::read_csv(paste0(dataFolder, "energy/gas/LSOA Gas csv/LSOA_GAS_2010.csv"))
dgas_LSOA_2019 <- readr::read_csv(paste0(dataFolder, "energy/gas/LSOA Gas csv/LSOA_GAS_2019.csv"))
dgas_LSOA_2010$dgas2010 <- dgas_LSOA_2010$`Mean consumption (kWh per meter)`
dgas_LSOA_2019$dgas2019 <- dgas_LSOA_2019$`Mean consumption (kWh per meter)`
merged_dgas <- merge(dgas_LSOA_2010, dgas_LSOA_2019, by = "Middle Layer Super Output Area (MSOA) Code", all = TRUE)
names(merged_dgas)
merged_dgas$dg_diff<-as.numeric(merged_dgas$dgas2019) - merged_dgas$dgas2010
summary(merged_dgas)
```

```{r Mapping the change in LSOA dom mean gas comsumption}
merged_dgas$LSOA11CD <- merged_dgas$"Middle Layer Super Output Area (MSOA) Code" #creating a variable with the LSOA code in the same name as in sf_data
lsoa_dgas20102019 <- merge(lsoa_sf_data, merged_dgas) #merging these
ggplot2::ggplot(merged_dgas) +
  geom_sf(aes(fill=dg_diff))+ 
  scale_fill_continuous(name="Change in Gas: Mean kWh per meter", low="green",high="red")+
  labs(caption ="Solent (all MSOAs)") ##BROKEN
```

#####Cities in more detail
```{r Southampton LSOA Gas}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(lsoa_merged_sf_gas, LAD11NM == "Southampton")

# plotting the gas consumption of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Winchester")
```
